No Replication Without Process Documentation:  An Assessment of Management

### 2019-11-08 MSE manuscript.Rmd
Fix number of published articles to final count of 151

| MSE type | Count |
|:--:|:--:|
| Published | 150 |
| Random Sample | 30 |
| Climate Change | 11 |  
*Estimated by extrapolating from the assessed MSEs to the full set for now, the submission will contain an final count.

>>>>

| MSE type | Count |
|:--:|:--:|
| Published | 151 |
| Random Sample | 30 |
| Climate Change | 11 |  
*Estimated by extrapolating from the assessed MSEs to the full set for now, the submission will contain an final count.
